% The formatting of this CV is based on @davidwhogg's layout.

\documentclass[12pt,letterpaper]{article}

\input{cvstyle}

\begin{document}\thispagestyle{empty}\sloppy\sloppypar\raggedbottom

\textbf{\Large Daniel Foreman-Mackey} \hfill
\textsf{\small foreman.mackey@gmail.com, http://dfm.io} \\[0.5ex]
Associate Research Scientist, Center for Computational Astronomy, Flatiron Institute\\[0.5ex]

\cvheading{Professional preparation}
\begin{list}{}{\cvlist}
\item
2017--, Associate Research Scientist, Flatiron Institute.
\item
2015--2017, Sagan Postdoctoral Fellow, University of Washington.
\item
PhD 2015, Department of Physics, New York University. Advisor: Hogg
\item
MSc 2010, Department of Physics, Queen's University, Canada. Advisor: Widrow
\item
BSc 2008, Department of Physics, McGill University, Canada.
\end{list}

\cvheading{Selected publications}
\begin{list}{}{\cvlist}
\input{pubs_select}
\end{list}

\cvheading{Popular open-source software}
\begin{list}{}{\cvlist}

\item {\bf emcee} ---
    MCMC sampling in Python. Popular in astronomy;
    the paper has over 1000 citations.
    \url{emcee.readthedocs.io}

\item {\bf george} ---
    Blazingly fast Gaussian processes for regression. Implemented in C++ and
    Python bindings. Joint work with applied mathematicians at NYU.
    \url{george.readthedocs.io}

\item {\bf celerite} ---
    Scalable computations for Gaussian process regression for one-dimensional
    problems.
    \url{celerite.readthedocs.io}

\item {\bf corner.py} ---
    Simple corner plots (or scatterplot matrices) in Python.
    \url{corner.readthedocs.io}

\end{list}

%\cvheading{Honors}
%\begin{list}{}{\cvlist}
%\item Kavli Fellow, 2015.
%\item Sagan Postdoctoral Fellowship, 2015--present.
%\item James Arthur Graduate Fellowship, 2014.
%\item Horizon Fellowship in the Natural \& Physical Sciences, 2012.
%\item Henry M. MacCracken Fellowship, 2010.
%\item NSERC Undergraduate Summer Research Award, 2007.
%\end{list}

\end{document}
