% The formatting of this CV is based on @davidwhogg's layout.

\documentclass[12pt,letterpaper]{article}

\input{cvstyle}

\begin{document}\thispagestyle{empty}\sloppy\sloppypar\raggedbottom

\textbf{\Large Daniel Foreman-Mackey} \hfill
\textsf{\small dfm@dfm.io, https://dfm.io} \\[0.5ex]
Research Scientist, Center for Computational Astrophysics, Flatiron Institute\\[0.5ex]

\subsection{Education}
\begin{list}{}{\cvlist}
  \item
        PhD 2015, Department of Physics, New York University. Advisor: Hogg
  \item
        MSc 2010, Department of Physics, Queen's University, Canada. Advisor: Widrow
  \item
        BSc 2008, Department of Physics, McGill University, Canada.
\end{list}

\subsection{Positions}
\begin{list}{}{\cvlist}
  \item
        Research Scientist, Flatiron Institute, 2022--present.
  \item
        Associate Research Scientist, Flatiron Institute, 2017--2022.
  \item
        Sagan Postdoctoral Fellow, University of Washington, 2015--2017.
\end{list}

\subsection{Popular open-source software}
\begin{list}{}{\cvlist}
  \input{repos}
\end{list}

\ifdefined\withpubs
  \subsection{Publications}
  \input{pubs_summary}

  \subsubsection{Refereed publications}
  \begin{list}{}{\cvlist}
    \input{pubs_ref}
  \end{list}

  \subsubsection{Preprints \& white papers}
  \begin{list}{}{\cvlist}
    \input{pubs_unref}
  \end{list}
\fi

\subsection{Selected invited talks \& tutorials}
\begin{list}{}{\cvlist}

  \item \emph{Methods for scalable probabilistic inference},
      2021, Invited Talk, Institute for Pure \& Applied Mathematics, UCLA.

  \item \emph{Advanced probabilistic modeling},
      2021, Tutorial, Harley Wood Winter School of Astronomy, Australia.

  \item \emph{Open-source software for probabilistic data analysis in astronomy},
      2021, Seminar, Instituto de Astrof\'isica, Portugal.

  \item \emph{Gaussian processes \& stellar variability},
      2021, Seminar, CARMENES Team Meeting.

  \item \emph{Extending JAX with custom C++ \& CUDA},
        2021, Invited Talk, IRIS-HEP Topical Meeting, CERN.

  \item \emph{Open source software for probabilistic data analysis},
        2020, Invited Talk, OzGrav Early Career Researcher Symposium, Australia.

  \item \emph{The why \& how of exoplanet, a domain-specific PyMC3 extension},
        2020, Contributed Talk, PyMC Con.

  \item \emph{A modular ecosystem for probabilistic data analysis},
        2019, Invited Talk, Open Digital Infrastructure in Astronomy conference,
        Kavli Institute for Theoretical Physics.

  \item \emph{Exoplanet population inference, a tutorial},
        2019, Invited Talk, Exostar19 conference,
        Kavli Institute for Theoretical Physics.

  \item \emph{Astronomy as a testbed for statistical method development},
        2019, Colloquium, Center for Statistics and Machine Learning,
        Princeton.

  \item \emph{Data-driven discovery in the astronomical time domain},
        2018, Colloquium, Institute for Theory and Computation,
        Harvard-Smithsonian Center for Astrophysics.

  \item \emph{Data-driven discovery in the astronomical time domain},
        2018, Colloquium, University of California, Santa Cruz.

  \item \emph{A practical introduction to Gaussian Processes for astronomy},
        2017, Invited Talk, Statistical Challenges in Astrophysics,
        University of New South Wales, Australia.

  \item \emph{Data-driven discovery in the astronomical time domain},
        2017, Interdisciplinary Colloquium, CIERA, Northwestern University.

  \item \emph{Long-period transiting planets \& their population},
        2016, Invited talk, Exoplanets I, Davos.

  \item \emph{Long-period transiting planets \& their population},
        2016, Invited talk, Statistical Challenges of Modern Astrophysics,
        Carnegie Mellon.

  \item \emph{Long-period transiting planets \& their population}, 2016,
        Colloquium, Villanova.

  \item \emph{Scalable Gaussian processes \& the search for transiting
          exoplanets}, 2015, Data Science at the LHC, CERN, Geneva.

  \item \emph{Discovery \& characterization of transiting exoplanets \& their
          population}, 2015, Colloquium, University of Washington.

  \item \emph{Hierarchical inference for exoplanet population inference},
        2015, IAU Symposium, Honolulu.

  \item \emph{Data-driven models}, 2015, Extreme precision radial velocities,
        Yale.

  \item \emph{Population inference from noisy \& incomplete catalogs}, 2015,
        Local Group Astrostatistics, University of Michigan.

  \item \emph{Time series analysis, Gaussian Processes, and the search for
          exo-Earths},
        2014, PyData NYC conference, New York.

  \item \emph{Introduction to Gaussian Processes, probabilistic graphical
          models, and deep learning},
        2014, Astro Hack Week, University of Washington.

  \item \emph{An astronomer's introduction to Gaussian processes},
        2014, Bayesian Computing for Astronomical Data Analysis (Summer school at
        Penn State University).

\end{list}

\subsection{Grants}
\begin{list}{}{\cvlist}
  \item NSF-CDS\&E (PI: Agol)
        \emph{Development of fast, multi-dimensional Gaussian Processes for Exoplanet discovery and beyond},
        \$471,048.00, 2019--2022

  \item
        NSF-AAG (PI: Agol),
        \emph{Collaborative Research: Masses and architectures of (potentially
          habitable) exoplanet systems},
        \$491,950, 2016--2018

  \item
        K2 Guest Observer -- Cycle 3 (PI: Penny),
        \emph{Free-Floating and Bound Planet Mass Measurements with K2: Ground- and
          Space-Based Photometry, Event Detection and Modeling},
        \$84,000, 2016--2017

  \item
        K2 Guest Observer -- Cycle 3 (PI: Hogg),
        \emph{Ultra-precise photometry in crowded fields: A self-calibration
          approach},
        \$100,000, 2016--2017

  \item
        XSEDE (PI: Foreman-Mackey),
        \emph{A systematic search for transiting exoplanets using K2},
        100,000 CPU hours, 2015--2016
\end{list}


\subsection{Honors}
\begin{list}{}{\cvlist}

  \item Kavli Fellow, 2015.
  \item Sagan Postdoctoral Fellowship, 2015--2017.
  \item James Arthur Graduate Fellowship, 2014.
  \item Horizon Fellowship in the Natural \& Physical Sciences, 2012.
  \item Henry M. MacCracken Fellowship, 2010.
  \item NSERC Undergraduate Summer Research Award, 2007.

\end{list}

% \ifdefined\withpubs
%     \newpage
% \fi

\subsection{Professional service \& activities}
\begin{list}{}{\cvlist}
  \item Topic Editor --- Journal of Open Source Software
  \item Active Referee ---
        AAS Journals,
        MNRAS,
        PASP,
        A\&A,
        Journal of Statistical Software,
        Journal on Uncertainty Quantification,
        Journal of Open Source Software
  \item Panelist ---
        NSF, NASA, LSSTC
\end{list}

\end{document}
