\documentclass[11pt,letterpaper]{article}

\input{cvstyle}
\input{pubs_summary_macros}

\addtolength{\topmargin}{-0.2in}
\addtolength{\textheight}{0.4in}
\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{0.4in}

\begin{document}\thispagestyle{empty}\sloppy\sloppypar\raggedbottom

\textbf{\Large Daniel Foreman-Mackey} \\[0.5ex]
% \textsf{\small dfm@dfm.io, https://dfm.io} \\[0.5ex]
Research Scientist, Center for Computational Astrophysics, Flatiron Institute \\
\textsf{\small %
\href{mailto:dfm@dfm.io}{dfm@dfm.io} | %
\href{https://dfm.io}{dfm.io} | %
\href{https://github.com/dfm}{github.com/dfm} | %
\href{https://www.linkedin.com/in/dan-foreman-mackey/}{linkedin.com/in/dan-foreman-mackey} %
}\\[0.5ex]

% \subsection{Overview}

\vspace{1ex}
\begin{list}{}{\cvlist}
    \item Lead developer and core maintainer of many popular open source packages including \href{https://github.com/dfm/emcee}{\project{emcee}}, \href{https://github.com/dfm/tinygp}{\project{tinygp}}, \href{https://github.com/dfm/corner.py}{\project{corner.py}}, and \href{https://github.com/showyourwork/showyourwork}{\project{showyourwork}}; a full list can be found on \href{https://github.com/dfm}{GitHub}.
    % \item An expert user of JAX with 
    \item As of \pubsdate\footnote{Publication data collected from \href{https://ui.adsabs.harvard.edu/}{NASA Astrophysics Data System}}, published \pubsnumber\ refereed papers with \pubscitations\ total citations, and an h-index of \pubshindex; a complete listing can be found on \href{https://scholar.google.com/citations?user=oMqNbfsAAAAJ}{Google Scholar}.
\end{list}

\subsection{Experience}

\begin{list}{}{\cvlist}
    \item
        \textbf{Center for Computational Astrophysics, Flatiron Institute, New
        York, NY} \\
        {\color{numcolor} Sep 2022 -- present}\,
        \emph{Research Scientist} \\
        {\color{numcolor} Sep 2017 -- Sep 2022}\,
        \emph{Associate Research Scientist} \\
        Associate professor equivalent faculty member. 
        Co-leader of ``Astronomical Data'' group with a steady state of about 10 full time researchers; managed and mentored 8 postdoctoral research fellows, and 9 graduate student researchers.
        Developed, released, and maintain \href{https://github.com/exoplanet-dev}{\project{exoplanet}}, a suite of Python libraries for probabilistic inference with large astronomical time series datasets built on top of \project{PyMC}; and \href{https://github.com/dfm/tinygp}{\project{tinygp}}, a JAX-based Gaussian Process modeling framework with novel algorithms for scalable linear algebra.
        Co-developed and lead the maintenance of \href{https://github.com/showyourwork/showyourwork}{\project{showyourwork}}, a workflow management system for reproducible scientific publishing.
        Made contributions to large open source projects including \project{AstroPy}, \project{PyMC}, \project{JAX}, and \project{NumPyro}. 
        \\[1.5ex]

    \item
        \textbf{The Journal of Open Source Software} \\
        {\color{numcolor} Nov 2022 -- present}\,
        \emph{Associate Editor-in-Chief, Astrophysics \& Space Sciences} \\
        {\color{numcolor} Nov 2019 -- Nov 2022}\,
        \emph{Topic Editor, Astrophysics} \\
        Associate professor equivalent faculty member. \\[1.5ex]

    \item
        \textbf{Department of Astronomy, University of Washington, Seattle, WA} \\
        {\color{numcolor} Sep 2015 -- Sep 2017}\,
        \emph{NASA Sagan Postdoctoral Fellow} \\
        Postdoctoral research supported by prestigious and competitive national fellowship.
        Developed, released, and maintained \href{https://github.com/dfm/celerite}{\project{celerite}}, an exact structure-exploiting factorization and inversion algorithm with linear scaling for a class of matrices commonly encountered in Gaussian Process modeling, and a C++/Python library for its use.
        Co-advised 3 PhD student theses.
        \\[1.5ex]

    \item
        \textbf{Department of Physics, New York University, New York, NY} \\
        {\color{numcolor} Sep 2010 -- Sep 2015}\,
        \emph{Graduate Research Assistant} \\
        Developed, released, and maintained several high-impact open source projects including
        \href{https://github.com/dfm/emcee}{\project{emcee}}, the most widely used probabilistic programming tool in astrophysics with over 10,000 citations;
        \href{https://github.com/dfm/george}{\project{george}}, a C++-accelerated Python library for scalable Gaussian Processes regression using approximate linear algebra;
        \href{https://github.com/dfm/corner.py}{\project{corner.py}}, a popular plotting library for assessing probabilistic models with nearly 2000 citations;
        and
        \href{https://github.com/daft-dev/daft}{\project{daft}}, a \project{matplotlib} extension for generating publication-ready probabilistic graphical models.
        Led the discovery of more than 20 new planets orbiting stars outside our Solar System.
\end{list}

\subsection{Education}
\begin{list}{}{\cvlist}
  \item
        PhD 2015, Department of Physics, New York University. Advisor: Hogg
  \item
        MSc 2010, Department of Physics, Queen's University, Canada. Advisor: Widrow
  \item
        BSc 2008, Department of Physics, McGill University, Canada.
\end{list}

\end{document}
