% The formatting of this CV is based on @davidwhogg's layout.

\documentclass[12pt,letterpaper]{article}

\input{cvstyle}

\begin{document}\thispagestyle{empty}\sloppy\sloppypar\raggedbottom

\textbf{\Large Daniel Foreman-Mackey} \hfill
\textsf{\small foreman.mackey@gmail.com, http://dan.iel.fm} \\[0.5ex]
Sagan Postdoctoral Fellow, Astronomy Department, University of Washington\\[0.5ex]

\cvheading{Education}
\begin{list}{}{\cvlist}
\item
PhD 2015, Department of Physics, New York University. Advisor: Hogg
\item
MSc 2010, Department of Physics, Queen's University, Canada. Advisor: Widrow
\item
BSc 2008, Department of Physics, McGill University, Canada.
\end{list}

\cvheading{Positions}
\begin{list}{}{\cvlist}
\item
Sagan Postdoctoral Fellow, University of Washington, 2015--present.
\end{list}

\ifdefined\withpubs
    \cvheading{Publications}
    \input{pubs_summary}

    \cvheading{Refereed publications}
    \begin{list}{}{\cvlist}
    \input{pubs_ref}
    \end{list}

    \newpage
    \cvheading{Preprints \& white papers}
    \begin{list}{}{\cvlist}
    \input{pubs_unref}
    \end{list}
\fi

\cvheading{Selected invited talks \& tutorials}
\begin{list}{}{\cvlist}

\item \emph{Long-period transiting planets \& their population},
    2016, Seminar, Canadian Institute of Theoretical Astrophysics.

\item \emph{Long-period transiting planets \& their population},
    2016, Seminar, University of Birmingham.

\item \emph{Long-period transiting planets \& their population},
    2016, Invited talk, Exoplanets I, Davos.

\item \emph{Long-period transiting planets \& their population},
    2016, Invited talk, Statistical Challenges of Modern Astrophysics,
    Carnegie Mellon.

\item \emph{Long-period transiting planets \& their population}, 2016,
    Colloquium, Villanova.

\item \emph{Long-period transiting planets \& their population},
    2016, Seminar, University of Auckland.

\item \emph{Long-period transiting planets \& their population},
    2016, Seminar, Sydney Institute for Astronomy.

\item \emph{Long-period transiting planets \& their population},
    2016, Seminar, Princeton.

\item \emph{Scalable Gaussian processes \& the search for transiting
    exoplanets}, 2015, Data Science at the LHC, CERN, Geneva.

\item \emph{Discovery \& characterization of transiting exoplanets \& their
    population}, 2015, Colloquium, University of Washington.

\item \emph{Hierarchical inference for exoplanet population inference},
    2015, IAU Symposium, Honolulu.

\item \emph{Data-driven models}, 2015, Extreme precision radial velocities,
    Yale.

\item \emph{Population inference from noisy \& incomplete catalogs}, 2015,
    Local Group Astrostatistics, University of Michigan.

\item \emph{The search for single transits},
    2015, Sagan Fellows Symposium, Caltech.

\item \emph{Inferring exoplanet populations from noisy, incomplete catalogs},
    2015, TESS group meeting, MIT.

\item \emph{Inferring exoplanet populations from noisy, incomplete catalogs},
    2015, Institute for Advanced Study, Princeton.

\item \emph{Licenses in the wild},
    2015, AAS225, Seattle.

\item \emph{Time series analysis, Gaussian Processes, and the search for
            exo-Earths},
    2014, PyData NYC conference, New York.

\item \emph{An astronomer's introduction to Gaussian processes},
    2014, Astronomy Department, University of Texas, Austin.

\item \emph{Introduction to Gaussian Processes, probabilistic graphical
            models, and deep learning},
    2014, Astro Hack Week, University of Washington.

\item \emph{Inferring exoplanet populations from noisy, incomplete catalogs},
    2014, Physics Department, University of Delaware.

\item \emph{Hierarchical inference for astronomers},
    2014, Strasbourg Observatory, France.

\item \emph{An astronomer's introduction to Gaussian processes},
    2014, Bayesian Computing for Astronomical Data Analysis (Summer school at
    Penn State University).

\item \emph{An astronomer's introduction to Gaussian processes},
    2014, Harvard--Smithsonian Center for Astrophysics.

\item \emph{Practical data analysis using MCMC},
    2014, Astronomy Department, University of Hertfordshire.

\item \emph{Practical data analysis using MCMC},
    2013, Astronomy Department, UCSC.

\item \emph{From pixels to aliens (Public Talk)},
    2013, Astronomy on Tap, NYC.

\item \emph{Data analysis using MCMC},
    2013, Astronomy Department, Columbia University.

\item \emph{Data analysis using MCMC},
    2013, Physics Department, Vanderbilt University.
\end{list}

\cvheading{Popular open-source software}
\begin{list}{}{\cvlist}

\item {\bf emcee} ---
    MCMC sampling in Python. Popular in astronomy;
    the paper has 524 citations as of 2016-01-26.
    \url{dfm.io/emcee}

\item {\bf George} ---
    Blazingly fast Gaussian processes for regression. Implemented in C++ and
    Python bindings. Joint work with applied mathematicians at NYU.
    \url{dfm.io/george}

\item {\bf corner.py} ---
    Simple corner plots (or scatterplot matrices) in Python.
    \url{github.com/dfm/corner.py}

\end{list}

\cvheading{Grants}
\begin{list}{}{\cvlist}
\item
NSF-AAG (PI: Agol),
\emph{Collaborative Research: Masses and architectures of (potentially
    habitable) exoplanet systems},
\&491,950, 2016--2018
\item
K2 Guest Observer -- Cycle 3 (PI: Penny),
\emph{Free-Floating and Bound Planet Mass Measurements with K2: Ground- and
Space-Based Photometry, Event Detection and Modeling},
\$84,000, 2016--2017
\item
K2 Guest Observer -- Cycle 3 (PI: Hogg),
\emph{Ultra-precise photometry in crowded fields: A self-calibration
approach},
\$100,000, 2016--2017
\item
XSEDE (PI: Foreman-Mackey),
\emph{A systematic search for transiting exoplanets using K2},
100,000 CPU hours, 2015--2016
\end{list}


\cvheading{Honors}
\begin{list}{}{\cvlist}

\item Kavli Fellow, 2015.
\item Sagan Postdoctoral Fellowship, 2015--present.
\item James Arthur Graduate Fellowship, 2014.
\item Horizon Fellowship in the Natural \& Physical Sciences, 2012.
\item Henry M. MacCracken Fellowship, 2010.
\item NSERC Undergraduate Summer Research Award, 2007.

\end{list}

% \ifdefined\withpubs
%     \newpage
% \fi

\cvheading{Professional service \& activities}
\begin{list}{}{\cvlist}
\item MAST Users Group --- Member
\item American Astronomical Society --- Full Member
\item Active Referee ---
    AAS Journals,
    Journal of Statistical Software,
    Journal of Open Source Software
\end{list}

\end{document}
